Comparative Analysis of Legislative Complex Networks of Select North American and European Countries

### 2018-12-11 paper/paper.tex
updating paper

There is an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018. The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018. This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Sweden Democrats. This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018.

\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{}{}{}
\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{}{}{}

@@

Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.

@@

\section{Discussion}
For our project, we use legislative cosponsorship networks across the US and selected European countries to try to infer social relationships in government that may influence legislative behavior. How well officials work together has a direct impact on the efficiency and productivity of government. The dynamic social relationships between legislators - of forging new relationships and maintaining older established relationships - matter. Moreover, our generated outputs hints at past and ongoing events that impact legislative cosponsorships. For example, the drop in number of cosponsorships across different parties in 2014-2018 in Sweden reflects the events that unfolded during the 2014 general elections, 
We have uncovered some intriguing results. First, we notice that the average distance tends to increase as the world gets smaller. One interpretation of this result is that members tend to be more isolated and fewer are willing to cooporate outside of their local network. As the world gets larger, the friendship circles that define and maintain social relationships grow. As communication between legislators improves, links become increasingly more interconnected, and the relative distance between any two given legislators decreases. This underlying phenomenom is reflected in the comparison of clustering coefficients across countries. For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1. 
We also notice a outcome in the US assortativity graph. We expected partisanship between the democratic and republican party. However, the US graphs have an assortativity of around 0, which suggests that there exists much more bipartisanship than one would think.

>>>>

There is an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018. The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018. This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Sweden Democrats. This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018, seen in Figure \ref{fig:swe_ass_1988} and \ref{fig:swe_ass_2014}.

\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{swe_ass_1988}{Sweden Assortativity 1988-1991}
\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{swe_ass_2014}{Sweden Assortativity 2014-2018}

@@

% TO DO:
%---------------------------------------------------------------------------
Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.

@@

% ------------------------------------------------------------------------

\section{Discussion}
For our project, we use legislative cosponsorship networks across the US and selected European countries to try to infer social relationships in government that may influence legislative behavior. How well officials work together has a direct impact on the efficiency and productivity of government. The dynamic social relationships between legislators - of forging new relationships and maintaining older established relationships - matter. Moreover, our generated outputs hints at past and ongoing events that impact legislative cosponsorships. For example, the drop in number of cosponsorships across different parties in 2014-2018 in Sweden reflects the events that unfolded during the 2014 general elections, 
We have uncovered some intriguing results. First, we notice that the average distance tends to increase as the world gets smaller. One interpretation of this result is that members tend to be more isolated and fewer are willing to cooporate outside of their local network. As the world gets larger, the friendship circles that define and maintain social relationships grow. As communication between legislators improves, links become increasingly more interconnected, and the relative distance between any two given legislators decreases. This underlying phenomenom is reflected in the comparison of clustering coefficients across countries. For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1. 
We also notice extreme partisanship in the US senate, which is expected given the party division between the Republicans and Democrats, and reflect

Gordon Ramsay: "This SOUp, IS DRY!!!"
